Verification of the CVM algorithm with a Functional Probabilistic Invariant

### 2025-06-21 paper/main.tex
add Kuldeep's funding source

% TODO: put in everyone's names here
\author{Emin Karayel}{Technical University of Munich, School of Computation, Information and Technology, Germany}{me@eminkarayel.de}{https://orcid.org/0000-0003-3290-5034}{}
\author{Seng Joe Watt}{Institute for Infocomm Research (I$^2$R), A*STAR, Singapore}{Watt_Seng_Joe@i2r.a-star.edu.sg}{https://orcid.org/0000-0002-6883-4736}{Singapore NRF Fellowship Programme NRF-NRFF16-2024-0002}
\author{Yong Kiam Tan}{Institute for Infocomm Research (I$^2$R), A*STAR, Singapore \and Nanyang Technological University, Singapore}{yongkiam.tan@ntu.edu.sg}{https://orcid.org/0000-0001-7033-2463}{Singapore NRF Fellowship Programme NRF-NRFF16-2024-0002}
\author{Kuldeep S. Meel}{Georgia Institute of Technology \and University of Toronto}{meel@cs.toronto.edu}{https://orcid.org/0000-0001-9423-5270}{TODO}
\author{Derek Khu}{Institute for Infocomm Research (I$^2$R), A*STAR, Singapore}{derek_khu@i2r.a-star.edu.sg}{https://orcid.org/0009-0000-0293-0664}{TODO}

>>>>

% TODO: put in everyone's names here
\author{Emin Karayel}{Technical University of Munich, School of Computation, Information and Technology, Germany}{me@eminkarayel.de}{https://orcid.org/0000-0003-3290-5034}{}
\author{Seng Joe Watt}{Institute for Infocomm Research (I$^2$R), A*STAR, Singapore}{Watt_Seng_Joe@i2r.a-star.edu.sg}{https://orcid.org/0000-0002-6883-4736}{Singapore NRF Fellowship Programme NRF-NRFF16-2024-0002}
\author{Yong Kiam Tan}{Institute for Infocomm Research (I$^2$R), A*STAR, Singapore \and Nanyang Technological University, Singapore}{yongkiam.tan@ntu.edu.sg}{https://orcid.org/0000-0001-7033-2463}{Singapore NRF Fellowship Programme NRF-NRFF16-2024-0002}
\author{Kuldeep S. Meel}{Georgia Institute of Technology, United States \and  University of Toronto, Canada}{meel@cs.toronto.edu}{https://orcid.org/0000-0001-9423-5270}{Natural Sciences and Engineering Research Council of Canada (NSERC), funding reference [RGPIN-2024-05956]}
\author{Derek Khu}{Institute for Infocomm Research (I$^2$R), A*STAR, Singapore}{derek_khu@i2r.a-star.edu.sg}{https://orcid.org/0009-0000-0293-0664}{}
